An Efficient Feedback Calibration Algorithm for Direct Imaging Radio Telescopes

### 2016-05-03 cal_demo/ms.tex
minor tweaks of wording

The next step is to grid the calibrated electric field measurements to regularly spaced 
positions on the 2D plane of the ground, $\mathbf{r}_j$. 
MOFF uses the antenna patterns as the gridding 
kernel according to the software holography/A-transpose technique \citep{mor09,bha08}. 
Mathematically we can express the gridding operation as
\begin{equation}
E'_j=\sum_a W_a(\mathbf{r}_j-\mathbf{r}_a) E'_a(t)
\end{equation}
This 
achieves an optimal map \citep{teg97b} and places the data on a regular grid. Unlike 
traditional correlators which grid visibilities, the MOFF grids the electric fields directly. This 
operation must be performed for every time step, before any averaging of the data.

>>>>

The next step is to grid the calibrated electric field measurements to regularly spaced 
positions on the 2D plane of the ground, $\mathbf{r}_j$. 
MOFF uses the antenna patterns as the gridding 
kernel according to the software holography/A-transpose technique \citep{mor09,bha08}. 
Mathematically we can express the gridding operation as
\begin{equation}
E'_j=\sum_a W_a(\mathbf{r}_j-\mathbf{r}_a) E'_a(t)
\end{equation}
This 
achieves an optimal map \citep{teg97b} and places the data on a regular grid. Unlike 
traditional correlators which grid visibilities, the MOFF grids the electric field measurements directly. This 
operation must be performed for every sample, before any averaging of the data.
